Near Optimal Behavior with Approximate State Abstraction

### 2016-02-04 paper/abstract.tex
adding some changes to theory result

The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction. For instance, prohibitively difficult task representations can be condensed in such a way that essential information is preserved, and consequently, solutions are tractably computable. Because of the difficulty of acquiring perfect knowledge, agents must often perform approximate abstraction on the basis of incomplete knowledge. In this work, we investigate sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation. We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions. Additionally, we empirically demonstrate reduction in task complexity and bounded loss of optimality of behavior as knowledge becomes more approximate.

>>>>

The combinatorial explosion that plagues planning and \ac{RL} algorithms can be moderated using abstraction. Prohibitively difficult task representations can be condensed such that essential information is preserved, and consequently, solutions are tractably computable. However, perfect abstractions are often computationally intractable to compute and ineffective in environments where no two situations are exactly alike. For these reasons, we investigate approximate abstractions, which treat nearly-identical situations as equivalent. In this work, we characterize sufficient conditions for approximate abstractions that preserve near optimal behavior while reducing the complexity of the original task representation. We present theoretical guarantees of the quality of behaviors derived from four classes of approximate abstractions. Additionally, we empirically demonstrate reduction in task complexity and bounded loss of optimality of behavior as knowledge becomes more approximate.

% Old one:
% Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems. However, in natural environments, no two states are identical. This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.

%Because of the difficulty of acquiring perfect knowledge, agents must often perform approximate abstraction on the basis of incomplete knowledge.

% There are a variety of attractive characteristics of approximate abstractions.

### 2016-02-04 paper/introduction.tex
adding some changes to theory result

\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant, consequently enabling agents to solve considerably more complex problems. However, in natural environments, no two states are identical. This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.

@@

% Approximate abstraction
The thesis of this work is that that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy. Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers two benefits. First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}. Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.

>>>>

\section{Introduction}
Abstraction plays a fundamental role in learning. Through abstraction, intelligent agents may reason about only the salient features of their environment while ignoring what is irrelevant. Consequently, agents are able to solve considerably more complex problems than without the use of abstraction. However, perfect abstractions require complete knowledge that is often computationally intractable to compute. Furthermore, in natural environments, no two states are identical, so perfect abstraction is ineffective. To overcome these issues, we investigate the space of approximate abstractions that enable agents to treat sufficiently similar states as identical. This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.

% What is approx abstraction, why good.
%However, because of the difficulty of acquiring perfect knowledge, agents must often perform abstraction on the basis of incomplete knowledge. We call such abstractions {\it approximate}.

%Agents are often faced with imperfect knowledge, so abstracting using complete knowledge is infeasible. However, agents may still perform abstractions by treating sufficiently similar situations as identical. We call such an abstraction {\it approximate}.

%However, faced with imperfect knowledge, agents must often perform approximate abstractions on the basis of treating sufficiently similar situations as identical.

% One like "natural environment", "states aren't identical" sentence.
%However, in natural environments, no two situations are identical; approximate abstractions enable learning agents to treat sufficiently similar situations as equivalent.

% One like "approx abstract because of approx knowledge"

%This work characterizes the impact of combining ``sufficiently similar'' states in the context of planning and \ac{RL} in \acp{MDP}.

@@

% Approximate abstraction
The thesis of this work is that that aggregation of states on the basis of various approximate criteria incur only bounded error in the resulting policy. Relaxing the aggregation criteria from equality of quantities to $\varepsilon$-closeness offers three benefits. First, state aggregation algorithms that satisfy these criteria employ the sort of knowledge that we expect a planning or learning algorithm to approximate without fully solving the \ac{MDP}. Second, because the state-aggregation criteria are relaxed to approximate equality, methods that employ approximate equality are able to tune the aggressiveness of state aggregation all the while incurring bounded error.
\dnote{Pick a version of this (either sentence 1 or 2)}
Third, (1) approximate abstractions can achieve greater degrees of compression due to their relaxed criteria of equality. (2) In natural environments, no two states are identical, so approximate abstraction may be useful but exact abstraction is completely ineffective.
